Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-07-16 writing/DraftExposurePaper/DraftExposurePaper.Rmd
Add to draft

>>>>

#### Are our methods of assessing distance reasonable

[Spline vs. linear interpolation? Is 15 minutes adequate? Should we use shapefiles instead? IBTrACS probably has this (`rnoaa`).]

#### Are our methods of assessing rainfall reasonable

[Is three-day window reasonable? Probably should be. If we go larger, there's the problem of picking up things that aren't related to the storm. Storms to check-- Floyd (ET), Irene (ET), Lee (slow moving), Ike (for timing), Faye, Allison]

#### Are our methods of assessing wind speed reasonable
